### 2018-02-01 includes/appendix.tex
Typos in appendix.
appendix

In this section, we informally discuss how we established
equisatisfiability guarantees regarding the transformations provided in
\fuzzer{}. We assume that the reader is familiar with SMT-LIB
syntax. The transformations work over boolean, integer, string
literals and expressions, and regular expressions.

To shorten our proofs, we make the following simplifications:
\begin{enumerate}
  \item
    Since many of the operators can be expressed in terms of others,
    our proofs will only consider a subset of the operators. In
    particular we drop the following:
    \begin{itemize}
      \item \texttt{or} (boolean or)
      \item \texttt{=} for boolean expressions
      \item \texttt{<=}, \texttt{>}, \texttt{>=}
      \item \texttt{str.prefixof}, \texttt{str.suffixof}, \texttt{str.at}, \texttt{str.contains}
      \item \texttt{re.range}, \texttt{re.+}, \texttt{re.allchar}, \texttt{re.all}
    \end{itemize}

>>>>

In this section, we informally discuss how we established
equisatisfiability guarantees regarding the transformations provided
in \fuzzer{}.  The transformations work over boolean, integer, string
literals and expressions, and regular expressions. To shorten our
proofs, we make the following simplifications:

\begin{enumerate}
  \item
    Since many of the operators can be expressed in terms of others,
    our proofs will only consider a subset of the operators. In
    particular we drop the following from consideration:
    \begin{itemize}
      \item \texttt{or} (boolean or)
      \item \texttt{=} for boolean expressions
      \item \texttt{<=}, \texttt{>}, \texttt{>=}
      \item \texttt{str.prefixof}, \texttt{str.suffixof}, \texttt{str.at}, \texttt{str.contains}
      \item \texttt{re.range}, \texttt{re.+}, \texttt{re.allchar}, \texttt{re.all}
    \end{itemize}
